Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-11-12 RR_manuscript/Draft_RR.Rmd
commented out comments

SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.

JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models.

TR:TRUE?

@@

CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/

I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:

$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$

@@

TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS

>>>>

<!-- TR: SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW. -->

<!-- JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models. -->

@@

<!-- TR: CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/ -->

<!-- JC:I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:

$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$-->

@@

<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS-->
